---
title: "Stocks"
author: "Chelsea Ursaner"
date: "9/11/2018"
output:
  word_document: default
  html_document: default
---

### Setup

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message=FALSE, warning=FALSE)
if (!require("pacman")) install.packages("pacman")
pacman::p_load(tidyquant, stringr)
```

### Exploring tidyquant - https://cran.r-project.org/web/packages/tidyquant/vignettes/TQ01-core-functions-in-tidyquant.html 

```{r}
# looking at key ratios for Tesla
# tq_get lets you pull prices, financials, etc.
tq_get_options()

# pulling key ratios returns a two-column dataset. The 'data' column is a list
tesla_ratios_all <- tq_get("TSLA", get = "key.ratios")
tesla_ratios_all 
```

## Inspecting lists and practicing purrr
```{r}
# Working with lists
tesla_ratios_list <- tesla_ratios_all$data # this saves the list column as a new object - a list of 7
tesla_Financial <- tesla_ratios_all$data[1] # this creates a list of just the first sub section - a list of 1
tesla_Financial2 <- tesla_ratios_all$data[[1]] # this unnests the list. A data frame - 150 rows and 5 columns

# inspecting a list element
# look at the variable names in the raw data
names(tesla_Financial2) 
# save it as a factor
tesla_Financial2$sub.section <- as.factor(tesla_Financial2$sub.section)
# look at the unique values in sub section
levels(tesla_Financial2$sub.section)
# the ratios in Financial are not split into sub-sections

# inspecting Growth ratios
tesla_Growth <- tesla_ratios_all$data[[2]]
levels(as.factor(tesla_Growth$sub.section))
levels(as.factor(tesla_Growth$category)) # see all of the ratios

glimpse(tesla_Growth) # see how the data is formatted

# Creating named lists
# Step 1 - do it for one
tesla_Growth_levels <- levels(as.factor(tesla_Growth$sub.section))

# Step 2 - make it a recipe
# I want to get a list of the distinct ratios for each section
# first try with just map
subsection_levels <- map(tesla_ratios_all$data, ~levels(as.factor(.x$sub.section))) #yay!!!

# Main list I want - all categories of ratios
tesla_ratios_all$categories <- map(tesla_ratios_all$data, ~levels(as.factor(.x$category))) 
tesla_ratios_all # now it's a list column

# make a new named list using the section names 
categories <- map(tesla_ratios_all$data, ~levels(as.factor(.x$category))) %>%
 set_names(tesla_ratios_all$section) 
# YAYY!!! So much easier than I realized

# export list to look at
print(categories[1:7])
```

### More practice - making a tibble
```{r}
# Pulling multiple stocks from tidyquant
test <- tq_get(c("TSLA", "DATA"), get = "key.ratios")
# This results in a tibble with the stock repeated 7 times for each section
names(test)

# Making a tibble
stocks_tbl <- tibble(
  name    = levels(as.factor(test$symbol)),
  Ratios   = "this shall be a list?")
```


### Test some code - pulling and visualizing indicators for TSLA

```{r eval=F}
# Pull the indicators I care about for one stock - TSLA
# Pull an entire section
tesla_ratios <- tesla_ratios_all %>%
    filter(section == "Valuation Ratios") %>%
    unnest() 

# Visualize the different ratios within that section 
tesla_ratios %>%
    ggplot(aes(x = date, y = value)) +
    geom_line(aes(col = factor(category, levels = c("Price to Earnings", "Price to Cash Flow", "Price to Book", "Price to Sales"))), 
              size = 1)  + 
    labs(title = "10-Year Historical Valuation Ratios for TSLA", x = "", 
         y = "", col = "") +
    theme_tq() +
    scale_color_tq()
```

## Applying purrr 

### Make my Portfolio Dataset with All the Data
```{r}
# Pull key ratios 
# specify the stock - this will be the .x
stock = "TSLA"

key_ratios <- tq_get(stock, get = "key.ratios") # results in a tibble
```


### Run first recipe - pulling all the tidyquant information for multiple stocks

```{r}
# Read TD Ameritrade stocks as a list
stocks <- (str_split("AMZN
ANSS
ASCMA
BDFFX
BEXFX
C
CS
DAL
DATA
DDD
GLIBA
KGFHY
KROTY
KW
LEXEA
LGF.B
LSXMA
LSXMK
LTRPA
MANH
PATI
PRMTX
RSTAY
SMCI
SSP
SSYS
SU
TM
TSLA
UA
UAA
WCN", pattern="\n"))

# make a smaller subset
stocks_subset <- head(stocks[[1]])
glimpse(stocks)

# turn it into a recipe - ex. map(people, ~ length(.x$starships))
# remember I can hover over map to see the arguments. map(.x, .f)
# for the [list, vector, column, dataframe!.. hence .x], do [.f] 
# map(stocks_subset, ~ tq_get(.x, "key_ratios"))
# test my recipe!
key_ratios2 <- map(stocks_subset, ~ tq_get(.x, "key_ratios")) # results in a list of six

# inspect my new list! 
key_ratios2[1:2] #look at the first two list items
# not helpful
# let's name it something that makes sense. What did I do/what was I going for with this list?
my_portfolio_subset <- key_ratios2 %>%
  set_names(stocks_subset)
# That worked! my_portfolio_subset is now a named list of 6 stocks
# Each stock is a tibble 
# Each tibble has a list column called data that is a data frame of all the ratios over time 
```

### Make and run second recipe - Extract a key metric from each stock - Return on Investment 
```{r}
# start with one - TSLA
# 1. extract a filtered dataframe of all the ROIs over time
tesla_ROI <- as.data.frame(tesla_ratios_all$data[2]) %>%
                             filter(category == "Return on Invested Capital %") %>%
  select(-1,-2) %>%
  rename(key_ratio = category)
                           
glimpse(levels(as.factor(tesla_ROI$category)))

# Take the average 
tesla_avg_ROI <- mean(tesla_ROI$value, na.rm=T)
# Save it as a percentage
tesla_avg_ROI <- round((mean(tesla_ROI$value, na.rm=T))/100,2)

# condense it
avg_ROI <- round(tesla_avg_ROI/100,2)

# Make my recipe
# map(.x, ~f) - for each stock, calculate its return on invested capital
my_portfolio_Profitability <- map(my_portfolio_subset, ~ (.x$data[[2]])) 

my_portfolio_ROI <- map(my_portfolio_Profitability, ~filter(.x, category == "Return on Invested Capital %"))

my_portfolio_avg_ROI <- map(my_portfolio_ROI, ~round((mean(.x$value, na.rm=T))/100,2))
my_portfolio_avg_ROI
```

### Make third recipe - Pull key indicators and compile them into a tibble

```{r}
# Now I have a list of stocks in the format I want it to look like. 
# Time to make the data what I want - extract key indicators

# Start with one - TSLA 
tesla_ratios_all

## Indicator group 1 - Financials
# Share Price, Revenue, and Earnings per Share most recent values
tesla_i1 <- tesla_ratios_all %>%
    filter(section == "Financials") %>%
    unnest()  %>% 
  filter(!is.na(date)) %>% 
  group_by (category) %>%
  slice(which.max(date)) %>%
  filter(group %in% c(1, 6, 10)) %>% 
  select(category, value) 
tesla_i1$value <- as.numeric(as.character(tesla_i1$value))

## Next section - Profitability
# Bunch of indicators
tesla_i2 <- tesla_ratios_all %>%
    filter(section == "Profitability") %>%
    unnest()  %>% 
  filter(!is.na(date)) %>% 
  group_by (category) %>%
  slice(which.max(date)) %>%
  arrange(group) %>%
  filter(group %in% c(18, 20, 22, 25, 26, 27:31)) %>% 
  select(category, value)

# Next section- growth. All the indicators!
tesla_i3 <- tesla_ratios_all %>%
    filter(section == "Growth") %>%
    unnest()  %>% 
  filter(!is.na(date)) %>% 
  group_by (category) %>%
  slice(which.max(date)) %>%
  select(category, value)

# Last group of indicators- Valuation Ratio
# Just Price to Earnings for now
tesla_i4 <- tesla_ratios_all %>%
    filter(section == "Valuation Ratios") %>%
    unnest()  %>% 
  filter(!is.na(date)) %>% 
  group_by (category) %>%
  slice(which.max(date)) %>%
  filter(group == 86) %>% 
  select(category, value)

# Check price to earnings just for fun
tesla_i1[1,2]/tesla_i1[2,2]
tesla_i4[1,2] # Hm.. doesn't match. Oh well

# Make final tibble for TSLA
TSLA <- rbind(tesla_i1, tesla_i2, tesla_i3, tesla_i4)
TSLA$category <- as.character(TSLA$category)
TSLA$value <- as.numeric(TSLA$value)
TSLA
```

### Compile tibbles into a named list - My Indicators
```{r}
# Make my recipe

# Fist for one section
test <- map(my_portfolio_subset, ~ (.x %>%
  filter(section == "Financials") %>%
    unnest()  %>% 
  filter(!is.na(date)) %>% 
  group_by (category) %>%
  slice(which.max(date)) %>%
  filter(group %in% c(1, 6, 10)) %>% 
  select(category, value) %>%
    mutate(Indicator = as.character(category), Value = as.numeric(value)) %>%
   select(Indicator, Value)))
glimpse(test[1])

# Now for the whole thing
my_indicators <- map(my_portfolio_subset, ~ rbind((.x %>%
    filter(section == "Financials") %>%
    unnest()  %>% 
  filter(!is.na(date)) %>% 
  group_by (category) %>%
  slice(which.max(date)) %>%
  filter(group %in% c(1, 6, 10)) %>% 
  select(category, value)),
  (.x %>%
    filter(section == "Profitability") %>%
    unnest()  %>% 
  filter(!is.na(date)) %>% 
  group_by (category) %>%
  slice(which.max(date)) %>%
  arrange(group) %>%
  filter(group %in% c(18, 20, 22, 25, 26, 27:31)) %>% 
  select(category, value)),
  (.x %>%
    filter(section == "Growth") %>%
    unnest()  %>% 
  filter(!is.na(date)) %>% 
  group_by (category) %>%
  slice(which.max(date)) %>%
  select(category, value)),
  (.x %>%
    filter(section == "Valuation Ratios") %>%
    unnest()  %>% 
  filter(!is.na(date)) %>% 
  group_by (category) %>%
  slice(which.max(date)) %>%
  filter(group == 86) %>% 
  select(category, value))
))
```

## Done! View List
```{r}
print(my_indicators)
```